Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
shorter through midway through section III

We present the approach taken to guide this study by
following the Goal-Question-Metric (GQM) methodology described by Basili et 
al.~\cite{Basili84}.

\vspace{1ex}
\noindent\textbf{Goal.}
The goal of this study is to identify and understand the relationship 
between the social factors that describe the
developer's experience (stars, followers, etc.) and technical properties that
describe the commit's complexity
(files added, files modified, etc.)
when predicting the likelihood that a developer's commit
will pass the continuous integration build tests for the project.

@@

\textbf{Do social attributes, gathered 
from developers' GitHub profiles ,
allow for more accurate predictions of 
the developer's build success
than only technical attributes?}

If social attributes improve the prediction of build success, then we are
interested in investigating how certain attributes, such as the developer's
follower count, correlates with build success.

\vspace{1ex}
\noindent\textbf{Metric.} We measure quality software contributions based on the
build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to identify
important factors in predicting build success;  decision tress are well
established and interpretable. In particular, we use a J48 decision tree because
this classifier has the ability to identify which attributes 
discriminate the various instances most clearly, and we are interested in
analyzing which features can be used to predict build success.
We first build a
decision tree classifier using only technical factors to determine
how well commit complexity predicts build integration
success.  We then include the social factors in the classification problem to 
identify the degree to which the social factors improve the model's predictive
power.
We evaluate the models with 10-fold cross-validation.

@@

\vspace{1ex}
\noindent\textbf{Technical Factors.} We collected technical factors from the 
Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy a commit's
complexity, such as commit size. 
The technical factors used are:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn, changed lines of code.
\item Files added by this commit.
\item Files modified by this commit.
\item Tests added by this commit.
\item Tests deleted by this commit.
\item Total source files in project at the time of the commit.
\item Source lines of source code in the project at
	the time of the commit.
\item Travis status, or status of the Travis build integration.
\end{itemize}

@@

\vspace{1ex}
\noindent\textbf{Social Factors.} We created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the
commit web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline
%
We scraped the commit author's
\textit{username} from each commit page, and then
collected the following from the user's public profile:
%(\textit{https://github.com/\textbf{UserName}}). 
%

\begin{itemize}
	\item Number of repositories the developer can access (including those
the developer owns, contributes
		to, and for which the developer has organizational membership
		access).%
\footnote{https://developer.github.com/v3/repos/}
\item  Number of projects the developer has stared. Starring a project
to shows approval of the repository and creates a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Number of developers that follow the author. 
\item Number of developers that the author follows.
\item Number of contributions made by the author in the last year.
\end{itemize}

@@

\hline
\end{tabular}
\\
\center
	\caption{\label{resultsTable}Comparison of predictive power by running 10-fold
    cross-validation of two decision trees with a non-downsampled dataset
	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled
	(4\textsuperscript{th} and 5\textsuperscript{th} column). 
	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
	%Zack: the above sentence isn't true for the second row.
	}   
\end{table*}
To address our main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?", we 
created a decision tree classifier~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. The decision trees were evaluated using 10-fold 
cross-validation with the data in each data set.

>>>>

We present the approach taken to guide this study by
following the Goal-Question-Metric (GQM) methodology~\cite{Basili84}:

\vspace{1ex}
\noindent\textbf{Goal.}
The \emph{goal} of this study is to identify and understand the relationship 
between the social factors that describe the
developer's experience (stars, followers, etc.) and technical properties that
describe a commit's complexity
(files added, files modified, etc.)
when predicting the likelihood that a developer's commit
will pass the continuous integration build tests for the project.

@@

\vspace{1ex}
\noindent \emph{Do social attributes, gathered from developers' GitHub profiles, allow for
  more accurate predictions of the developer's build success than only technical
  attributes?}

If social attributes improve build success predication, we are
interested in investigating how particular attributes, such as the developer's
follower count, similarly correlate with success.

\vspace{1ex}
\noindent\textbf{Metric.} We measure software contribution quality by the
build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to identify
important factors in predicting build success;  decision trees are well
established and interpretable. We use a J48 decision tree, which
has the ability to identify which attributes 
discriminate the various instances most clearly.
We first build a
decision tree classifier using only technical factors to 
predict build integration
success.  We then include the social factors, to 
identify the degree to which the social factors improve the model's predictive
power.
We evaluate the models with 10-fold cross-validation.

@@

\vspace{1ex}
\noindent\textbf{Technical Factors.} We collected technical factors from the 
Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
We extracted the following techical attributes as proxy to a commit's
complexity: 
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn, changed lines of code.
\item Files added by this commit.
\item Files modified by this commit.
\item Tests added by this commit.
\item Tests deleted by this commit.
\item Total source files in project at the time of the commit.
\item Number of source lines of code in the project at
	the time of the commit.
\item Travis status, or status of the Travis build integration.
\end{itemize}

@@

\vspace{1ex}
\noindent\textbf{Social Factors.} We created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the 
MSR Challenge~\cite{msr17challenge} dataset to locate the
commit web page, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline
%
We scraped the commit author's
\textit{username} from each commit page to
collect the following from the user's public profile:
%(\textit{https://github.com/\textbf{UserName}}). 
%

\begin{itemize}
	\item Number of repositories the developer can access (including those
the developer owns, contributes to, or for which they have
organizational membership access).%
\footnote{https://developer.github.com/v3/repos/}
\item  Number of projects the developer has stared. Starring a project
to shows approval of the repository and creates a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Number of developers that follow the author. 
\item Number of developers that the author follows.
\item Number of contributions made in the last year.
\end{itemize}

@@

\hline
\end{tabular}
\\
\center
	\caption{\label{resultsTable} Predictive power 
      decision trees with a non-downsampled dataset
	(2\textsuperscript{nd} and 3\textsuperscript{rd} column) and downsampled
	(4\textsuperscript{th} and 5\textsuperscript{th} column). 
	%The higher the percentages represent the higher number of instances we are able to correctly predict. \label{resultsTable}
	%Zack: the above sentence isn't true for the second row.
	}   
\end{table*}
To address our main research question: ``Do social attributes, gathered 
from the GitHub profiles of developers,
allow for more accurate predictions than only using technical data?", we 
created a decision tree classifier~\cite{Quinlan86}.
Decision trees are a predictive model which uses binary decisions on the
attributes to predict a final class.  The predicted class is represented as the
leaves, while the attribute decisions used in the prediction cause the
different branches.
In this study, we used the Weka J48 decision tree~\cite{Weka,Quinlan1993}
with default settings. The decision trees were evaluated using 10-fold 
cross-validation with the data in each data set.
